Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-10-01 vertical-thermal-review_SI.Rmd
Update vertical-thermal-review_SI.Rmd
fixed headers & TOC

---
title: 'Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications'
output:
  word_document:
    toc: true
    toc_depth: 2
bibliography: Zotero_references.bib
csl: new-phytologist.csl

@@

# MAIN MANUSCRIPT DISPLAY ITEMS  (limit 8)
#figures
fig_schematic = 1
fig_NEON_vertical =  2
fig_leaf_T = 3
fig_treerings= 4 
fig_model=5

@@

##  `r appendix_NEON_methods_title`

@@

# Study sites
We analyzed vertical gradients in key biophysical variables from the National Ecological Observatory Network's Airborne Observatory Platform (NEON AOP) and meteorology towers at six focal NEON sites [Figs 2, S1, @schimelNEONHierarchicallyDesigned2007]. The sites are well distributed across the United States and represent key forest types and structures (Table S1).

# Estimating forest and light environments from lidar

@@

# Analyzing biophysical gradients from micrometeorological data

@@

##  `r appendix_tealeaves_methods_title`

@@

\newpage
## References

>>>>

---
title: 'Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications'
output:
  word_document:
    toc: true
    toc_depth: 1
bibliography: Zotero_references.bib
csl: new-phytologist.csl

@@

# MAIN MANUSCRIPT DISPLAY ITEMS  (limit 8)
#figures
fig_schematic = 1
fig_NEON_vertical =  2
fig_leaf_T = 3
fig_treerings= 4 
fig_ecosystem=5
fig_model=6

@@

#  `r appendix_NEON_methods_title`

@@

## Study sites
We analyzed vertical gradients in key biophysical variables from the National Ecological Observatory Network's Airborne Observatory Platform (NEON AOP) and meteorology towers at six focal NEON sites [Figs 2, S1, @schimelNEONHierarchicallyDesigned2007]. The sites are well distributed across the United States and represent key forest types and structures (Table S1).

## Estimating forest and light environments from lidar

@@

## Analyzing biophysical gradients from micrometeorological data

@@

#  `r appendix_tealeaves_methods_title`

@@

\newpage
# References
